---
layout: topic
title: Getting Help	
---
	
### I am stuck... I get an error message that I don't understand

Start by googling the error message. However, this doesn't always work very well
because often, package developers rely on the error catching provided by R. You
end up with general error messages that might not be very helpful to diagnose a
problem (e.g. "subscript out of bounds").

However, you should check stackoverflow. Search using the `[r]` tag. Most
questions have already been answered, but the challenge is to use the right
words in the search to find the answers:
[http://stackoverflow.com/questions/tagged/r](http://stackoverflow.com/questions/tagged/r)

The [Introduction to R](http://cran.r-project.org/doc/manuals/R-intro.pdf) can
also be dense for people with little programming experience but it is a good
place to understand the underpinnings of the R language.

The [R FAQ](http://cran.r-project.org/doc/FAQ/R-FAQ.html) is dense and technical
but it is full of useful information.

### Asking for help

The key to get help from someone is for them to grasp your problem rapidly. You
should make it as easy as possible to pinpoint where the issue might be.

Try to use the correct words to describe your problem. For instance, a package
is not the same thing as a library. Most people will understand what you meant,
but others have really strong feelings about the difference in meaning. The key
point is that it can make things confusing for people trying to help you. Be as
precise as possible when describing your problem

If possible, try to reduce what doesn't work to a simple reproducible
example. If you can reproduce the problem using a very small `data.frame`
instead of your 50,000 rows and 10,000 columns one, provide the small one with
the description of your problem. When appropriate, try to generalize what you
are doing so even people who are not in your field can understand the question.

To share an object with someone else, if it's relatively small, you can use the
function `dput()`, it will output R code that can be used to recreate the exact same
object as the one in memory:

```{r, results='show'}
dput(head(iris)) # iris is an example data.frame that comes with R
```

If the object is larger, provide either the raw file (i.e., your CSV file) with
your script up to the point of the error (and after removing everything that is
not relevant to your issue). Alternatively, in particular if your questions is
not related to a `data.frame`, you can save any R object to a file:

```{r, eval=FALSE}
saveRDS(iris, file="/tmp/iris.rds")
```

The content of this file is however not human readable and cannot be posted
directly on stackoverflow. It can how be sent to someone by email who can read
it with this command:

```{r, eval=FALSE}
some_data <- readRDS(file="~/Downloads/iris.rds")
```

Last, but certainly not least, **always include the output of `sessionInfo()`**
as it provides critical information about your platform, the versions of R and
the packages that you are using, and other information that can be very helpful
to understand your problem.

```{r, results='show'}
sessionInfo()
```

### Where to ask for help?

* Your friendly colleagues: if you know someone with more experience than you,
  they might be able and willing to help you.
* Stackoverlow: if your question hasn't been answered before and is well
  crafted, chances are you will get an answer in less than 5 min.
* The [R-help](https://stat.ethz.ch/mailman/listinfo/r-help): it is read by a
  lot of people (including most of the R core team), a lot of people post to it,
  but the tone can be pretty dry, and it is not always very welcoming to new
  users. If your question is valid, you are likely to get an answer very fast
  but don't expect that it will come with smiley faces. Also, here more than
  everywhere else, be sure to use correct vocabulary (otherwise you might get an
  answer pointing to the misuse of your words rather than answering your
  question). You will also have more success if your question is about a base
  function rather than a specific package.
* If your question is about a specific package, see if there is a mailing list
  for it. Usually it's included in the DESCRIPTION file of the package that can
  be accessed using `packageDescription("name-of-package")`. You may also want
  to try to email the author of the package directly.
* There are also some topic-specific mailing lists (GIS, phylogenetics, etc...),
  the complete list is [here](http://www.r-project.org/mail.html).

### More resources

* The [Posting Guide](http://www.r-project.org/posting-guide.html) for the R
  mailing lists.
* [How to ask for R help](http://blog.revolutionanalytics.com/2014/01/how-to-ask-for-r-help.html)
  useful guidelines
